\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{fontspec}  % Include this to use system fonts

% Set the font to Arial
\setmainfont{Arial}

\definecolor{maincolor}{HTML}{2E86C1}
\hypersetup{
    colorlinks=true,
    urlcolor=maincolor,
    linkcolor=maincolor
}

\titleformat{\section}{\large\bfseries\color{maincolor}}{}{0em}{}
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[ -- ]
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Md Rifath Hassan}} \\
    \vspace{1mm}
    Address: Federal Territory of Kuala Lumpur, Malaysia \\ 
    \href{mailto:mhrifath92@gmail.com}{Email: mhrifath92@gmail.com} 
    \href{tel:+60104225051}{Mobile: +60104225051}
    \href{https://www.linkedin.com/in/md-rifath-hassan/}{LinkedIn: linkedin.com/in/md-rifath-hassan/} \quad
    \vspace{1mm}
\end{center}

\section*{Professional Summary}
Strategic and detail-oriented IT Project Manager with over 2 years of experience successfully planning, executing, and delivering web, mobile, and enterprise software projects across Asia-Pacific. Adept in Agile and Scrum methodologies, with a strong command of the full software development lifecycle (SDLC), risk management, and stakeholder engagement. Proven ability to lead cross-functional remote teams, optimize workflows, and ensure timely delivery of high-quality digital solutions within scope and budget. Proficient in project management tools such as Jira, Confluence, Trello, Git, and Asana, with a focus on aligning technical execution with business objectives to drive measurable results.

\section*{Professional Experience}
\subsection*{IT Project Manager | MIB Promotions}
\textit{May 2024 – Present} \\

\begin{itemize}
    \item Delivered 10+ end-to-end software and web projects across industries, achieving 95\% on-time delivery and client satisfaction.
    \item Led Agile workflows using Jira and ClickUp, increasing team productivity by 30\% through streamlined sprint planning, daily stand-ups, and retrospectives.
    \item Coordinated cross-functional teams of developers, designers, and QA engineers, reducing development cycle time by 25\%.
    \item Maintained consistent stakeholder communication with weekly demos and reports, improving transparency and trust across all accounts.
    \item Implemented structured task tracking and backlog grooming, resulting in a 40\% drop in task-related delays. 
\end{itemize}

\subsection*{\textbf{Remote Project Manager} | TrueTel, Melbourne- Australia}
\textit{May 2023 – March 2024} \\
\begin{itemize}
    \item Supported project delivery for telecom software solutions by preparing detailed timelines, risk assessments, and scope documentation.
    \item Monitored project progress across 5+ concurrent initiatives, ensuring optimal use of resources and reducing bottlenecks by 20\%.
    \item Assisted in agile ceremonies and client reviews, contributing to a 15\% improvement in client feedback integration.
    \item Maintained project documentation in Confluence and Git, standardizing reporting and enhancing version control accuracy by 30\%.
    \item Played a key role in refining project scopes, helping reduce scope creep and maintaining a 90\% delivery-to-plan ratio. 
\end{itemize}

\subsection*{\textbf{IT Project Management Executive} | Al-Hamaed Medical Company (HMC), Saudi Arabia}
\textit{March 2019 – March 2023} \\

\begin{itemize}
    \item Assisted in managing IT projects for pharmaceutical operations, including inventory and CRM systems.
    \item Coordinated with vendors and teams for ERP integration and system upgrades.
    \item Supported process automation and user training to enhance operational efficiency. 
\end{itemize}

\subsection*{\textbf{Digital Product Management} | Grameenphone Ltd. Dhaka- Bangladesh}
\textit{Dec 2016 – Nov 2018} \\
\begin{itemize}

    \item Managed the entire lifecycle of digital products, from concept to launch, improving delivery speed by 30\%.
    \item Collaborated with cross-functional teams to define product roadmaps and prioritize features using Agile/Scrum.
    \item Led user research and data analysis, increasing engagement by 25\% through iterative improvements.
    \item Launched self-service platforms that reduced support calls by 40\%. 
\end{itemize}

\section*{Core Skills}
\begin{tabbing}
\hspace{3cm} \= \kill
\textbf{Project Planning} : Agile, Scrum, Kanban, SDLC, Risk Management, Budget \& Resource Allocation  \\
\textbf{Tools:} Jira, ClickUp, Trello, Asana, Notion, MS Project, Git, Confluence \\
\textbf{Technical Understanding:} Web \& Mobile Applications, APIs, Cloud Services, PostgreSQL, MySQL, Basic Docker, \\QA \& Testing Workflows\\
\textbf{Soft Skills:} Team Leadership, Stakeholder Management, Communication \& Reporting, Remote Collaboration,\\Client Relationship Management, Team Collaboration, Usability Testing, User Research,\\ Product Lifecycle Management, Digital Platform Optimization. \\
\textbf{Development Knowledge:} Front-end Web , JavaScript, Python, Django, Django Rest framework \\
\end{tabbing}

\section*{Education}
\textbf{MSc in Information Technology} \\
City University, Malaysia \\
\textit{2024 – Present}

\textbf{BSc in Computer Science Engineering} \\
City University of Bangladesh, Dhaka-Bangladesh \\
\textit{2012 – 2016}\\

\section*{Certifications}
\textbf{Digital Product Management–} Ostad \\
\textbf{Certified Scrum Master (CSM)}\\
\textbf{Google Project Management Certificate}\\
\textbf{PRINCE2 Project Management–} Alison \\

\section*{Key Projects}
\textbf{CRM System Development–}  \\
Led the end-to-end development of a custom CRM web application for a finance client. Managed a 5-person team and delivered the platform within a deadline and budget, improving the efficiency of tracking client leads by 60\% and allowing real-time sales reporting.\\
\textbf{E-Learning Platform Redesign–} \\
Oversaw the complete redesign and migration of a university’s e-learning platform. Enhanced user experience and system performance by 40\%, reduced page load times by 50\%, and increased student engagement metrics within the first month after launch.\\
\textbf{Mobile Booking App–} \\
Delivered the MVP of a cross-platform mobile booking app in just 3 sprints using Agile Scrum. Reduced the time to market for the client by 40\% and improved the efficiency of the booking process through streamlined UX and automated notifications.\\

\end{document}
